The effects of linkage disequilibrium on maintaining balanced polymorphisms in seasonal adaptation

### 2019-12-04 writing/manuscript.Rmd
greatest version

Quantitative genetic theory suggests that plasticity occurs in response to selective pressure exerted by environmental heterogeneity [@Cooper2010].  Phenotypic plasticity is especially beneficial in variable environments because genetic variability allows for adaptation to changing conditions [@Gulisija2016]. Fluctuating selection can maintain polymorphisms in seasonal environments if strong selective pressure towards both homozygous genotypes varies seasonally [@Novak2017, @Bergland2014].Seasonality can drive powerful selection fluctuations, especially for organisms which have short a generation time of less than a month [@Messer2016]. Understanding the role of seasonality on adaptation can allow more accurate predictions to be made about the capacity for organisms to adapt to climate change conditions [@Fournier-Level2016].

@@

Our model recreates and builds upon the work of @Wittman2017 to understand how linkage disequilibrium contributes to maintaining polymorphisms in a natural population. We study how rate of crossover, epistasis, number of generation per season, population size, allelic dominance, and seasonal balance contributes to segregation lift. Finally, we test how allelic interactions effect the dynamics of seasonal adaptation.

>>>>

Quantitative genetic theory suggests that plasticity occurs in response to selective pressure exerted by environmental heterogeneity [@Cooper2010].  Phenotypic plasticity is especially beneficial in variable environments because genetic variability allows for adaptation to changing conditions [@Gulisija2016]. Fluctuating selection can maintain polymorphisms in seasonal environments if strong selective pressure towards both homozygous genotypes varies seasonally [@Novak2017, @Bergland2014]. Seasonality can drive powerful selection fluctuations, especially for organisms which have short a generation time of less than a month [@Messer2016]. Understanding the role of seasonality on adaptation can allow more accurate predictions to be made about the capacity for organisms to adapt to climate change conditions [@Fournier-Level2016].

@@

Our model recreates and builds upon the work of @Wittman2017 to understand how linkage disequilibrium contributes to maintaining polymorphisms in a natural population. We study how the rate of crossover, epistasis, number of generation per season, population size, allelic dominance, and seasonal balance contribute to segregation lift. Finally, we test how allelic interactions effect the dynamics of seasonal adaptation.
